---
title: "Tutorial"
author: "TLB"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Use this command to install the package. When prompted, enter '3' to skip updates.

``` {r, eval=FALSE}
devtools::install_github("tbrock0122/tlb.project")
```

Don't forget to read in the package as well.

```{r}
library(tlb.project)
```

# Easy Analysis

This package is meant to streamline the process of performing simple statistical analyses using linear data. Namely, performing linear regression analyses and analyses of variance between two variables in a data set. Both of these analyses are quite useful in determining if there are statistically significant relationships/interactions between the different kinds of data you may be taking in a project, and are commonly used for introductory biostatistics.


## Function 1 - linear_regression
Simple linear regressions are used to determine the relationship between a response variable and a single numerical predictor variable. This function allows you to fit your chosen data to a linear model, perform the regression, and print the resulting statistics to the screen in a single line of code. Simply provide which columns of data you'd like to investigate, making sure that variable_2 is numerical data.

```{r}
file_path <- system.file("extdata", "Data.csv", package="tlb.project")
Data <- read.csv(file_path)

linear_regression(Data$Estimated_Age, Data$SVL)
```
## Function 2 - linear_regression_full
Function 2 is very similar to Function 1 in that both use the same inputs and both perform a linear regression, though the outputs are completely different. This function checks if the residuals from the linear regression have a normal distribution, and prints a Normal Q-Q Plot to the screen for us to interpret. The closer the data lie to the line, the more normal the distribution.


```{r}
linear_regression_full(Data$Estimated_Age, Data$SVL)

```
In this example, the majority of the data lie on or close to the line, implying normality, though the values at the lower extreme do show greater deviation due to the hypothetical data supplied. 


## Function 3 - simple_anova

Analyses of variance (ANOVAs) are used to determine the relationship between a response variable and a single categorical predictor variable, whereas the previous regression functions used a numerical predictor. Again, all you need to provide are the data columns you want to investigate, then the function will perform the ANOVA and print out the ANOVA table to the screen.

```{r}
simple_anova(Data$SVL, Data$Life_Stage)

```