---
title: "Tutorial"
author: "TLB"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Use this command to install the package. When prompted, enter '3' to skip updates.

``` {r, eval=FALSE}
devtools::install_github("tbrock0122/tlb.project")
```

Don't forget to read in the package as well.

```{r}
library(tlb.project)
```

## Easy Analysis

This package is meant to streamline the process of performing simple statistical analyses using linear data. Namely, performing linear regression analyses and analyses of variance between two variables in a data set. 

provide rationale for why someone might need to do this analysis. explain how functions work (e.g. what types of data used, what outputs are, what's expected for inputs)

## Linear Regression Analysis

# Function 1 - linear_regression
Simple linear regressions are used to determine the relationship between a response variable and a single numerical predictor variable. This function allows you to fit your chosen data to a linear model, perform the regression, and print the resulting statistics to the screen in a single line of code. Simply provide which columns of data you'd like to investigate, making sure that variable_2 is numerical data.

```{r}
file_path <- system.file("extdata", "Data.csv", package="tlb.project")
Data <- read.csv(file_path)

linear_regression(Data$Estimated_Age, Data$SVL)
```



```{r}

```
# Analysis of Variance (ANOVA)

Simple ANOVA are used to determine the relationship between a response variable and a single categorical predictor variable.

```{r}
simple_anova(Data$SVL, Data$Life_Stage)

```